Formalization of Forcing in Isabelle/ZF \thanks{Supported by Secyt-UNC project 33620180100465CB and Conicet.}

### 2019-12-28 IJCAR2020/absoluteness.tex
enumeración de (algunos) avances por sobre Separation
ToDo list, typos, nuevos archivos

The concepts of relativization and absoluteness (due to Gödel, in his
proof of the relative consistency of $\AC$ \cite{godel-L}) 
are both
prerrequisites and powerful tools in working with transitive
models. The \emph{relativization} $\phi^C(\bx)$ of a set-theoretic
definition
$\phi$ (of relation such
as ``$x$ is a subset of $y$'' or of a function like $y=\P(x)$) to
a class $C$ is obtained by taking its (first-order) definition and
restricting all of its quantifiers to $C$.

@@

>>>>

The concepts of relativization and absoluteness (due to Gödel, in his
proof of the relative consistency of $\AC$ \cite{godel-L}) 
are both
prerrequisites and powerful tools in working with transitive
models. The \emph{relativization} $\phi^C(\bx)$ of a set-theoretic
definition
$\phi$ (of a relation such
as ``$x$ is a subset of $y$'' or of a function like $y=\P(x)$) to
a class $C$ is obtained by taking its (first-order) definition and
restricting all of its quantifiers to $C$.

@@

[New absoluteness results on powersets (/ universes?)]

### 2019-12-28 IJCAR2020/conclusion.tex
ToDo list, typos, nuevos archivos

>>>>

TODO:
\begin{enumerate}
\item Implement \emph{Basic Set Theory (BST)} by Kunen in
  Constructible: the use of alternatively Replacement or Powerset to
  prove basic absoluteness and closure resuls.
\item Enhance the automatization of formulas
\item Develop the forcing notions to obtain the independence of $\CH$,
  along with the prerrequisite combinatorial results (v.g.\ the
  $\Delta$-system lemma).
\end{enumerate}
